\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
sorted the authors alphabetically

Since then it has been developed and maintained by a development team: in alphabetical order,
Emanuele Casarotti,
Min Chen,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Jes\'us Labarta,
Dimitri Komatitsch,
Qinya Liu,
Yang Luo,
Nicolas Le Goff,
Pieyre Le Loher,
Alessia Maggi,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp.\\

>>>>

Since then it has been developed and maintained by a development team: in alphabetical order,
Emanuele Casarotti,
Min Chen,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp.\\
